### 2016-07-15 main.tex
Adding summary

\documentclass[12pt,twoside]{report}
%% Decomment next line to use PostScript fonts
%%\UsePackage{times}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                    %%
%%                    ***   I M P O R T A N T   ***                   %%
%%                                                                    %%
%% Fill in the following fields with the required information:        %%
%%  - \department{...}  name of the graduate department               %%
%%  - \degree{...}      name of the degree obtained                   %%
%%  - \author{...}      name of the author                            %%
%%  - \title{...}       title of the thesis                           %%
%%  - \gyear{...}       year of graduation                            %%
%%  - \super{...}    supervisor
%%  - \firstname, \middlename, \lastname... there is additional documentation by the actual fields, so I'll leave it at that
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{appendix}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[byname]{smartref}
\usepackage{hyperref} %comment out for hardcopy
\usepackage{txfonts}
\usepackage{tocloft}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{times}
\usepackage{float}
%\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
\usepackage[flushleft]{threeparttable}
\usepackage{pgffor}
\usepackage{chapterbib}
\usepackage{mwe}    % loads »blindtext« and »graphicx«
\usepackage{subfig}
\usepackage{slantsc}
\usepackage[latin1]{inputenc}   
\usepackage[T1]{fontenc}   
\usepackage[finnish]{babel}
\makeatletter
\numberwithin{figure}{chapter}
\newenvironment{acknowledgements}%
{\clearemptydoublepage
 \begin{center}
  \section*{Acknowledgements}
 \end{center}
 \begingroup
}{\newpage\endgroup}

@@

\newcommand\acknowlege[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Acknowledgements\normalsize\\\indent\\#1\newpage
  \fi
}
\newcommand\dedications[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Dedication\normalsize\\\indent\\#1\newpage
  \fi
}
%\renewcommand{\appendixtocname}{\Huge \textbf{List of Appendices} \normalsize}
\newcommand{\blank}{\hspace{-2mm}}
\newcommand{\super}{Dr. P. M. Barmby} %supervisor
\newcommand{\sco}{Dr. E. Peeters}  %member of supervisory committee
\newcommand{\sct}{Dr. G. Osinski}  %other member of supervisory committee (lbin)
\newcommand{\examo}{Dr. R. Abraham}  %examining committee (up to four, if less leave blank)
\newcommand{\examt}{Dr. M. Daley}
\newcommand{\examth}{Dr. S. C. Gallagher}
\newcommand{\examf}{Dr. P. Wiegert}
\newcommand{\department}{Physics and Astronomy}
\newcommand{\degree}{Doctor of Philosophy}
\newcommand{\firstname}{Sahar}
%\newcommand{\middlename}{}
\newcommand{\lastname}{Rahmani}
%\renewcommand{\author}[1]{\ifx\empty#1\else\gdef\@author{#1}\fi} 
\newcommand{\authorname}{{\firstname} {\middlename} {\lastname}}
\newcommand{\titl}{What governs star formation in galaxies? A modern statistical approach}
\newcommand{\spinetitle}{Extragalactic star formation}%only if the above is more than 60 characters
\newcommand{\thesisformat}{Integrated Article} %or Integrated Article
\newcommand{\gyear}{\number\year}
\newcommand{\makecoauthor}{
%Type information about coauthorship here/
Thanks to Sophia, Hossein and Els. 
}
\newcommand{\makeacknowlege} { 1) Pauline
2) Els, Sophia, Hossein,
3)I would like to thank all my Friends in Western. Neven, dave, Matt, parshati, sina, zahra, fereshteh, aycha, maryam, Laura, Taylor, dimuthu, Sham, ghazal, pubu, robin, Hoori, Javad, ali, shanon, Mohad, Boshra
4) bacheha
5) western ppl; Jodi, Brian, Henry, Phin,...
6) Mohad, shahin, pejman, pouria, masood,babak
7) fako famil
}
\newcommand{\makededications} {
To my parents, my sisters, and Matin, for their unconditional love and support. 
}
\newcommand{\listappendixname}{List of Appendices}
\newlistof{myappendices}{app}{\listappendixname}
\newcommand{\myappendices}[1]{%
\addcontentsline{app}{myappendices}{#1}\par}

@@

>>>>

\documentclass[12pt,twoside]{report}
%% Decomment next line to use PostScript fonts
%%\UsePackage{times}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                    %%
%%                    ***   I M P O R T A N T   ***                   %%
%%                                                                    %%
%% Fill in the following fields with the required information:        %%
%%  - \department{...}  name of the graduate department               %%
%%  - \degree{...}      name of the degree obtained                   %%
%%  - \author{...}      name of the author                            %%
%%  - \title{...}       title of the thesis                           %%
%%  - \gyear{...}       year of graduation                            %%
%%  - \super{...}    supervisor
%%  - \firstname, \middlename, \lastname... there is additional documentation by the actual fields, so I'll leave it at that
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{appendix}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[byname]{smartref}
\usepackage{hyperref} %comment out for hardcopy
\usepackage{txfonts}
\usepackage{tocloft}
\bibliographystyle{apj}
\usepackage{natbib}
\usepackage{times}
\usepackage{float}
%\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
%\usepackage{booktabs,fixltx2e}
\usepackage[flushleft]{threeparttable}
\usepackage[T1]{fontenc}

\makeatletter
\numberwithin{figure}{chapter}
\newenvironment{acknowledgements}%
{\clearemptydoublepage
 \begin{center}
  \section*{Acknowledgements}
 \end{center}
 \begingroup
}{\newpage\endgroup}

@@

\newcommand\acknowlege[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Acknowledgements\normalsize\\\indent\\#1\newpage
  \fi
}
\newcommand\dedications[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Dedication\normalsize\\\indent\\#1\newpage
  \fi
}
%\renewcommand{\appendixtocname}{\Huge \textbf{List of Appendices} \normalsize}
\newcommand{\blank}{\hspace{-2mm}}
\newcommand{\super}{Dr. P. M. Barmby} %supervisor
\newcommand{\sco}{Dr. E. Peeters}  %member of supervisory committee
\newcommand{\sct}{Dr. G. Osinski}  %other member of supervisory committee (lbin)
\newcommand{\examo}{Dr. R. Abraham}  %examining committee (up to four, if less leave blank)
\newcommand{\examt}{Dr. M. Daley}
\newcommand{\examth}{Dr. S. C. Gallagher}
\newcommand{\examf}{Dr. P. Wiegert}
\newcommand{\department}{Physics and Astronomy}
\newcommand{\degree}{Doctor of Philosophy}
\newcommand{\firstname}{Sahar}
%\newcommand{\middlename}{}
\newcommand{\lastname}{Rahmani}
%\renewcommand{\author}[1]{\ifx\empty#1\else\gdef\@author{#1}\fi} 
\newcommand{\authorname}{{\firstname} {\middlename} {\lastname}}
\newcommand{\titl}{What governs star formation in galaxies? A modern statistical approach}
\newcommand{\spinetitle}{Extragalactic star formation}%only if the above is more than 60 characters
\newcommand{\thesisformat}{Integrated Article} %or Integrat
\newcommand{\gyear}{\number\year}
\newcommand{\makecoauthor}{
%Type information about coauthorship here/
The work presented in this thesis has greatly benefited from advice by my supervisor Dr. Pauline Barmby and collaborators: Dr. Sofia Lianue, Dr. Hossein Teimoorinia, and Dr. Els Peeters. Although I led the projects, performed the analysis and wrote the manuscripts, their suggestions and feedback on the analyses and manuscripts were greatly helpful.

{\bf Chapter 2}: Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation, has been published in the Monthly Notices of the Royal Astronomical Society, Volume 456, Issue 4, 2016.

{\bf Chapter 3}: Data Mining in Nearby Galaxies, will be submitted in the near future.

{\bf Chapter 4}: Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach, has been submitted to The Monthly Notices of The Royal Astronomical Society.
}
\newcommand{\makeacknowlege} { 1) Pauline
2) Els, Sophia, Hossein,
3)I would like to thank all my Friends in Western. Neven, dave, Matt, parshati, sina, zahra, fereshteh, aycha, maryam, Laura, Taylor, dimuthu, Sham, ghazal, pubu, robin, Hoori, Javad, ali, shanon, Mohad, Boshra
4) bacheha
5) western ppl; Jodi, Brian, Henry, Phin,...
6) Mohad, shahin, pejman, pouria, masood,babak
7) fako famil
}
\newcommand{\makededications} {
To my parents, my sisters, and Matin, for their unconditional love and support. 
}
\newcommand{\listappendixname}{List of Appendices}
\newlistof{myappendices}{app}{\listappendixname}
\newcommand{\myappendices}[1]{%
\addcontentsline{app}{myappendices}{#1}\par}

@@

ed Article
\newcommand{\gyear}{\number\year}
\newcommand{\makecoauthor}{The work presented in this thesis has greatly benefited from advice by my supervisor Dr. Pauline Barmby and collaborators: Dr. Sofia Lianue, Dr. Hossein Teimoorinia, and Dr. Els peeters. Although I led the projects, performed the analysis and wrote the manuscripts, my worked greatly benefited from their suggestions and feedback on the analyses and manuscripts in chapters 2,3, and 4.\\
Chapter 2: Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation, has been published in the Monthly Notices of the Royal Astronomical Society, Volume 456, Issue 4, 2016.\\
Chapter 3: Data Mining in Nearby Galaxies, will be submitted in the near future.\\
Chapter 4: Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach, has been submitted to The Monthly Notices of The Royal Astronomical Society
}
\newcommand{\makeacknowlege} { 1) Pauline
2) Els, Sophia, Hossein,
3)I would like to thank all my Friends in Western. Neven, dave, Matt, parshati, sina, zahra, fereshteh, aycha, maryam, Laura, Taylor, dimuthu, Sham, ghazal, pubu, robin, Hoori, Javad, ali, shanon, Mohad, Boshra
4) bacheha
5) western ppl; Jodi, Brian, Henry, Phin,...
6) Mohad, shahin, pejman, pouria, masood,babak
7) fako famil
}
\newcommand{\makededications} {
To my parents, my sisters, and Matin, for their unconditional love and support. 
}
\newcommand{\listappendixname}{List of Appendices}
\newlistof{myappendices}{app}{\listappendixname}
\newcommand{\myappendices}[1]{%
\addcontentsline{app}{myappendices}{#1}\par}

 \import{../version0.0/}{intro0.0}
% \include{paper1}
% %\include{paper3}
% \include{paper2}
% \include{summary}

### 2016-07-15 version0.0/appendixa.tex
Adding summary

\chapter{Appendix}
\section{SFR from H$\alpha$ plus 24 \um: procedure and result}
\label{app:halpha}

As mentioned in Section~\ref{sec:data}, we used the H$\alpha$ data from the Nearby Galaxies Survey \citep{Massey07} to create one of our SFR maps. These data cover 10 overlapping fields across the disk of M31 in broad and narrow bands and were observed between August 2000 and September 2002; we obtained them  from the NOAO Science Archive. Making a spatially resolved SFR map of M31 using H$\alpha$ emission requires removal of background and stellar emission in each field, masking out foreground stars and saturated regions, creating a mosaic of H$\alpha$ continuum-subtracted images, and finally correcting for the flux contribution to the \halpha filter from the [N II] 6583~\AA\ line.

@@

To create the final mosaic, first we removed the background from each region in both the \halpha and $R$-band images. The second step was to subtract the continuum from the \halpha images. Since both \halpha and $R$-band images were aligned on the same coordinate grid, for each field, the R-band image multiplied by the scaling factor was subtracted from each corresponding \halpha image. At the end, we masked out all the foreground and saturated regions which include a $10\arcmin \times 10\arcmin$ region in the centre of the galaxy. To account for the flux contribution of the [N II] emission we used the flux ratio ${\rm [NII]}/{\rm H}\alpha = 0.54$ from \citet{Kennicutt08}, and subtracted it from the \halpha map. We created the final mosaic image, Figure~\ref{fig:halpha}, using the Montage program \citep{Berriman08}.

Creating the SFR map using \halpha plus 24 \um was described in Section~\ref{sec:sfr_halpha}. In order to investigate the SFR laws, we used the same method of the fitting as Section~\ref{sec:fitting}. The fitting results using SFR(\halpha $+$ 24~\um) are more or less the same as the other two SFR tracers. The main reason for this difference is the missing data in the centre of the galaxy and the lack of smooth background in the \halpha data. Thus we did not include the SFR(\halpha $+$ 24 \um) in our final analysis.

@@

\section{Results of training for one-dimensional self-organizing maps}
\label{app: high_Z_1d_soms}
As mentioned in Sec.~\ref{sec: 1D}, we changed the size of the SOM from $1\times2$ to $1\times22$. In that section we show some example of the results, here we show the rest of the maps to monitor the changes in the map in various sizes.

\label{app: 1d}
    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_4.png}
            %\caption{$1\times4$ weight map}
             %\label{fig: 1by4T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_4.png}
             %\caption{$1\times4$ hits map}
             %\label{fig: 1by4Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times4$~grid.}
         \label{fig: 1by4T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_5.png}
            %\caption{$1\times5$ weight map}
             %\label{fig: 1by5T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_5.png}
             %\caption{$1\times5$ hits map}
             %\label{fig: 1by5Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times5$~grid.}
         \label{fig: 1by5T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_6.png}
            %\caption{$1\times6$ weight map}
             %\label{fig: 1by6T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_6.png}
             %\caption{$1\times6$ hits map}
             %\label{fig: 1by6Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times6$~grid.}
         \label{fig: 1by6T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_7.png}
            %\caption{$1\times7$ weight map}
             %\label{fig: 1by7T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_7.png}
             %\caption{$1\times7$ hits map}
             %\label{fig: 1by7Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times7$~grid.}
         \label{fig: 1by7T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_8.png}
            %\caption{$1\times8$ weight map}
             %\label{fig: 1by8T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_8.png}
             %\caption{$1\times8$ hits map}
             %\label{fig: 1by8Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times8$~grid.}
         \label{fig: 1by8T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_9.png}
            %\caption{$1\times9$ weight map}
             %\label{fig: 1by9T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_9.png}
             %\caption{$1\times9$ hits map}
             %\label{fig: 1by9Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times9$~grid.}
         \label{fig: 1by9T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/dist_1_by_10.png}
            %\caption{$1\times10$ weight map}
             %\label{fig: 1by10T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/hit_t_1_by_10.png}
             %\caption{$1\times10$ hits map}
             %\label{fig: 1by10Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times10$~grid.}
         \label{fig: 1by10T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/dist_1_by_11.png}
            %\caption{$1\times11$ weight map}
             %\label{fig: 1by11T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/hit_t_1_by_11.png}
             %\caption{$1\times11$ hits map}
             %\label{fig: 1by11Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times11$~grid.}
         \label{fig: 1by11T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/dist_1_by_12.png}
            %\caption{$1\times12$ weight map}
             %\label{fig: 1by12T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/hit_t_1_by_12.png}
             %\caption{$1\times12$ hits map}
             %\label{fig: 1by12Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times12$~grid.}
         \label{fig: 1by12T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/dist_1_by_15.png}
            %\caption{$1\times15$ weight map}
             %\label{fig: 1by15T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/hit_t_1_by_15.png}
             %\caption{$1\times15$ hits map}
             %\label{fig: 1by15Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times15$~grid.}
         \label{fig: 1by15T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/dist_1_by_20.png}
            %\caption{$1\times20$ weight map}
             %\label{fig: 1by20T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/hit_t_1_by_20.png}
             %\caption{$1\times20$ hits map}
             %\label{fig: 1by20Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times20$~grid.}
         \label{fig: 1by20T}
    \end{figure}

>>>>

\chapter{SFR from H$\alpha$ plus 24 \um: procedure and result}
\pagestyle{plain}
\label{app:halpha}
\myappendices{
As mentioned in Section~\ref{sec:data}, we used the H$\alpha$ data from the Nearby Galaxies Survey \citep{Massey07} to create one of our SFR maps. These data cover 10 overlapping fields across the disk of M31 in broad and narrow bands and were observed between August 2000 and September 2002; we obtained them  from the NOAO Science Archive. Making a spatially resolved SFR map of M31 using H$\alpha$ emission requires removal of background and stellar emission in each field, masking out foreground stars and saturated regions, creating a mosaic of H$\alpha$ continuum-subtracted images, and finally correcting for the flux contribution to the \halpha filter from the \nii\ 6583~\AA\ line.

@@

To create the final mosaic, first we removed the background from each region in both the \halpha and $R$-band images. The second step was to subtract the continuum from the \halpha images. Since both \halpha and $R$-band images were aligned on the same coordinate grid, for each field, the R-band image multiplied by the scaling factor was subtracted from each corresponding \halpha image. At the end, we masked out all the foreground and saturated regions which include a 10\arcmin $\times$ 10\arcmin region in the centre of the galaxy. To account for the flux contribution of the [N II] emission we used the flux ratio ${\mathrm \nii}/{\mathrm H}\alpha = 0.54$ from \citet{Kennicutt08}, and subtracted it from the \halpha map. We created the final mosaic image, Figure~\ref{fig:halpha}, using the Montage program \citep{Berriman08}.

Creating the SFR map using \halpha plus 24 \um was described in Section~\ref{sec:sfr_halpha}. In order to investigate the SFR laws, we used the same method of the fitting as Section~\ref{sec:fitting}. The fitting results using SFR(\halpha $+$ 24~$\mu$m) are more or less the same as the other two SFR tracers. The main reason for this difference is the missing data in the centre of the galaxy and the lack of smooth background in the \halpha data. Thus we did not include the SFR(\halpha $+$ 24~$\mu$m) in our final analysis.

@@

}
